### 2024-04-12 paper/paper.qmd
Partial writing of Data section

---
title: "My title"
subtitle: "My subtitle if needed"
author: Allen Uy
thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

# Introduction

Anime refers to animation originating from Japan. In 2021, half of Netflix's 222 million subscribers watched some anime on the platform and viewership saw an increase of 20% in the total hours over the previous year [@netflixAnime].

MyAnimeList, herein referred to as MAL, is one of the largest and most popular anime database and communities online. Users are able to keep track of anime they have watched or plan to, as well as rate and find similar anime.

We conduct an analysis on the ratings of anime on MAL. Specifically we contrast

# Data {#sec-data}

The data in this paper is sourced from the MAL API [@MALAPI] and was gathered on April 10, 2024. The rankings of anime in the database are updated twice a day so the data gathered can be assumed to be up to date. Data analysis is performed in R [@citeR] with help from the following libraries: `tidyverse` [@citeTidyverse], `arrow` [@citeArrow], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `testthat` [@citeTestthat], `here` [@citeHere], `knitr` [@citeKnitr], `kableExtra` [@citeKableExtra], `dotenv` [@citeDotenv], and `httr2` [@citeHttr2].

## Measurement

In order to rate anime and add them to a list users must register an account on the MAL website. Each account can add an anime to their list once by choosing 1 of 5 statuses: watching, completed, on-hold, dropped, and plan to watch. It is also possible to remove an anime from the list if it was added by mistake. Every user that has an anime on their list is counted as a member of that anime, which is how the popularity rank is calculated. The user can also give a score to an anime, regardless of status, which is an integer from 1 to 10. The score of an anime on MAL is a weighted score calculated as:

```{=tex}
\begin{equation}
\text{Weighted Score} = \left( \frac{v}{v + m} \right) \cdot S + \left( \frac{m}{v + m} \right) \cdot C
\end{equation}

where:
\begin{align*}
    & \text{Weighted Score} \text{ is the calculated score for the anime/manga.} \\
    & v \text{ is the number of users who have given a score for the anime/manga.} \\
    & m \text{ is the minimum number of scored users required to get a calculated score.} \\
    & S \text{ is the average score given by users to the anime/manga.} \\
    & C \text{ is the mean score across the entire anime/manga database.}
\end{align*}
```
This equation requires a minimum number of scores to ensures a fair sample size and takes into account popularity and normalizes the score compared to the mean score in the database. In addition, MAL verifies whether the user has viewed 1/5 of the series upon completion and excludes scores by illegitimate accounts that try to sway votes. How this is done is not detailed. Due to the personal nature of these lists we assume that each user and list is associated with exactly one individual.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-04-12 scripts/02-data_cleaning.R
Cleaned top 10000 anime. Converted genres to boolean.

@@ -1,44 +1,38 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the data obtained by the MAL API for easier processing
+# and saves to parquet
+# Author: Allen Uy
+# Date: 12 April 2024
+# Contact: allen.uy@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 01-download_data is run and file is saved in appropriate location
 
 #### Workspace setup ####
-library(tidyverse)
+library("tidyverse")
+library("arrow")
+library("janitor")
+
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- readRDS("data/raw_data/anime_rankings.rds")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+cleaned_data <- raw_data |> clean_names()
+
+# Extract all genres and convert to booleans
[…]

### 2024-04-13 scripts/02-data_cleaning.R
Added tests for cleaned data

@@ -5,7 +5,8 @@
 # Date: 12 April 2024
 # Contact: allen.uy@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 01-download_data is run and file is saved in appropriate location
+# Pre-requisites: 01-download_data is run and raw data is saved in 
+# appropriate location
 
 #### Workspace setup ####
 library("tidyverse")
@@ -22,14 +23,22 @@ cleaned_data <- raw_data |> clean_names()
 all_genres <- unique(unlist(cleaned_data$genres))
 
 for (genre in all_genres) {
-  cleaned_data[[genre]] <- 0
+  cleaned_data[[genre]] <- as.integer(0)
 }
 
 for (i in seq_len(nrow(cleaned_data))) {
   for (genre in cleaned_data$genres[[i]]) {
-    cleaned_data[i, genre] <- 1
+    cleaned_data[i, genre] <- as.integer(1)
   }
 }
+
+cleaned_data$id <- as.integer(cleaned_data$id)
+cleaned_data$rank <- as.integer(cleaned_data$rank)
+cleaned_data$popularity <- as.integer(cleaned_data$popularity)
+cleaned_data$start_date <- as.Date(cleaned_data$start_date)
+cleaned_data$num_scoring_users <- as.integer(cleaned_data$num_scoring_users)
+cleaned_data$num_list_users <- as.integer(cleaned_data$num_list_users)
+
 
 cleaned_data <- cleaned_data |> select(-genres) |>
   clean_names()

### 2024-04-13 scripts/03-test_data.R

@@ -1,15 +1,55 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests cleaned data to ensure robustness
+# Author: Allen Uy
+# Date: 12 April 2024
+# Contact: allen.uy@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-data_cleaning was run and cleaned data is saved in
+# appropriate location
 
 
 #### Workspace setup ####
-library(tidyverse)
-# [...UPDATE THIS...]
+library("tidyverse")
+library("testthat")
+library("arrow")
+library("here")
+
+clean_anime <- read_parquet(here::here("data/analysis_data/clean_anime.parquet"))
 
 #### Test data ####
+
+test_that("variables are expected type", {
+  expect_type(clean_anime$id, "integer")
+  expect_type(clean_anime$title, "character")
+  expect_type(clean_anime$rank, "integer")
+  expect_type(clean_anime$start_date, "Date") # When saving as parquet date type isn't preserved
+  expect_type(clean_anime$studio, "character")
+  expect_type(clean_anime$mean, "double")
+  expect_type(clean_anime$popularity, "integer")
+  expect_type(clean_anime$num_list_users, "integer")
+  expect_type(clean_anime$num_scoring_users, "integer")
+  expect_type(clean_anime$action, "integer")
+})
+
+test_that("values are unique", {
+  expect_equal(length(unique(clean_anime$id)), nrow(clean_anime), label = "Length of 'id' column matches the number of rows")
+  expect_equal(length(unique(clean_anime$rank)), nrow(clean_anime), label = "Length of 'rank' column matches the number of rows")
+  expect_equal(length(unique(clean_anime$popularity)), nrow(clean_anime), label = "Length of 'popularity' column matches the number of rows")
+})
+
+test_that("variables do not have null values", {
+  expect_false(anyNA(clean_anime$id), label = "No null values in 'id' column")
+  expect_false(anyNA(clean_anime$title), label = "No null values in 'title' column")
+  expect_false(anyNA(clean_anime$rank), label = "No null values in 'rank' column")
[…]

### 2024-04-13 paper/paper.qmd
Added data graphs

@@
 
-library(tidyverse)
+library("tidyverse")
+library("arrow")
+library("here")
+library("knitr")
+library("kableExtra")
+
+clean_anime <- read_parquet(here::here("data/analysis_data/clean_anime.parquet"))
 ```
@@
 Due to the personal nature of these lists we assume that each user and list is associated with exactly one individual.
+
+## Top 10000 Ranked Anime
+
+```{r, echo=FALSE}
+#| label: tbl-anime_dataset
+#| tbl-cap: Sample of Anime
+head(clean_anime, 5) %>% 
+  kable(
+    booktabs = TRUE,
+    linesep = ""
+  ) %>% kable_styling(latex_options = "scale_down")
+```
+
+```{r, echo=FALSE}
+#| label: fig-score_distribution
+#| fig-cap: Distribution of scores of top 10000 anime
+
+mean_score <- mean(clean_anime$mean)
+
+clean_anime %>%
+  ggplot(aes(x = mean)) +
+  geom_histogram(binwidth = 0.1, color="darkblue", fill="lightblue") +
+  theme_minimal() +
+  geom_vline(aes(xintercept=mean_score), linetype="dashed", size=1) +
+  annotate("text", x = mean_score + 0.1, y = 550, label = paste("Mean Score:", round(mean_score, 2)), 
+           hjust = 0, vjust = -1) +
+  labs(x = "Score", y = "count", title = "Distribution of scores of top 10000 anime")
+```
+
+```{r, echo=FALSE}
+#| label: fig-rank_vs_popularity
+#| fig-cap: Rank vs Popularity
+
+clean_anime |>  ggplot(aes(x = rank, y = popularity)) +
+  geom_point(color = "blue", size=0.5) +
+  labs(x = "Rank (Low to High)", y = "Popularity (Low to High)", title = "Rank vs Popularity") +
+  scale_x_reverse() +
+  scale_y_reverse() +
+  theme_minimal()
+```
 

### 2024-04-13 scripts/01a-download_data.R

@@ -1,0 +1,88 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data using the MyAnimeList API
+# Author: Allen Uy
+# Date: 12 April 2024
+# Contact: allen.uy@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: .env is placed in working directory with bearer token
+# refer to README for more details
+
+
+#### Workspace setup ####
+library("httr2")
+library("tidyverse")
+library("dotenv")
+
+Sys.unsetenv("BEARER_TOKEN")
+load_dot_env()
+BEARER_TOKEN <- Sys.getenv("BEARER_TOKEN")
+
+#### Obtain top ranked anime from MyAnimeList ####
+num_anime = 500
+total_anime = 20000
+fields="id,title,rank,start_date,mean,popularity,num_list_users,num_scoring_users,studios,genres"
+
+all_anime <- tibble(id=numeric(),
+                    title=character(),
+                    rank=numeric(),
+                    start_date=character(),
+                    studio=character(),
+                    mean=numeric(),
+                    popularity=numeric(),
+                    num_list_users=numeric(),
+                    num_scoring_users=numeric(),
+                    genres=list())
+
+for (n in 0:(total_anime/num_anime - 1)) {
+  req = request("https://api.myanimelist.net/v2/anime/ranking") |> 
+    req_url_query(ranking_type="all", limit=num_anime, offset=0+n*500, fields=fields) |>
+    req_auth_bearer_token(BEARER_TOKEN)
+  
+  resp <- req_perform(req)
+  
+  anime_json <- resp_body_json(resp)
+  
+  
+  for (i in 1:num_anime) {
+    anime <- anime_json$data[[i]]$node
+    
+    id <- anime$id
+    title <- anime$title
+    rank <- anime$rank
+    start_date <- anime$start_date
+    mean <- anime$mean
+    popularity <- anime$popularity
+    num_list_users <- anime$num_list_users
+    num_scoring_users <- anime$num_scoring_users
+    if (length(anime$studios) > 0) {
+      studio <- anime$studios[[1]]$name
+    }
+    
+    genres <- list()
+    for (j in 1:length(anime$genres)) {
+      genre <- anime$genres[[j]]$name
+      genres <- c(genres, list(genre))
+    }
+    
+    all_anime <- all_anime |> add_row(id=id,
+                                      title=title,
+                                      rank=rank,
+                                      start_date=start_date,
+                                      mean=mean,
+                                      popularity=popularity,
[…]

### 2024-04-13 scripts/01b-download_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data using the MyAnimeList API
 # Author: Allen Uy
-# Date: 10 April 2024
+# Date: 12 April 2024
 # Contact: allen.uy@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: .env is placed in working directory with bearer token
-# refer to README for more details
+# refer to README for more details. 01a-download_data is run.
 
 
 #### Workspace setup ####
@@ -17,95 +17,28 @@ Sys.unsetenv("BEARER_TOKEN")
 load_dot_env()
 BEARER_TOKEN <- Sys.getenv("BEARER_TOKEN")
 
-#### Obtain top ranked anime from MyAnimeList ####
-num_anime = 500
-total_anime = 10000
-fields="id,title,rank,start_date,mean,popularity,num_list_users,num_scoring_users,studios,genres"
-
-all_anime <- tibble(id=numeric(),
-                    title=character(),
-                    rank=numeric(),
-                    start_date=character(),
-                    studio=character(),
-                    mean=numeric(),
-                    popularity=numeric(),
-                    num_list_users=numeric(),
-                    num_scoring_users=numeric(),
-                    genres=list())
-
-for (n in 0:(total_anime/num_anime - 1)) {
-  req = request("https://api.myanimelist.net/v2/anime/ranking") |> 
-    req_url_query(ranking_type="all", limit=num_anime, offset=0+n*500, fields=fields) |>
-    req_auth_bearer_token(BEARER_TOKEN)
-  
-  resp <- req_perform(req)
-  
-  anime_json <- resp_body_json(resp)
-  
-  
-  for (i in 1:num_anime) {
-    anime <- anime_json$data[[i]]$node
-    
-    id <- anime$id
-    title <- anime$title
-    rank <- anime$rank
-    start_date <- anime$start_date
-    mean <- anime$mean
-    popularity <- anime$popularity
-    num_list_users <- anime$num_list_users
-    num_scoring_users <- anime$num_scoring_users
-    if (length(anime$studios) > 0) {
-      studio <- anime$studios[[1]]$name
-    }
-    
-    genres <- list()
-    for (j in 1:length(anime$genres)) {
-      genre <- anime$genres[[j]]$name
-      genres <- c(genres, list(genre))
-    }
-    
-    all_anime <- all_anime |> add_row(id=id,
-                                      title=title,
-                                      rank=rank,
-                                      start_date=start_date,
-                                      mean=mean,
[…]

### 2024-04-13 scripts/02-data_cleaning.R

@@ -5,7 +5,7 @@
 # Date: 12 April 2024
 # Contact: allen.uy@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 01-download_data is run and raw data is saved in 
+# Pre-requisites: 01a-download_data is run and raw data is saved in 
 # appropriate location
 
 #### Workspace setup ####
@@ -42,6 +42,10 @@ cleaned_data$num_list_users <- as.integer(cleaned_data$num_list_users)
 
 cleaned_data <- cleaned_data |> select(-genres) |>
   clean_names()
+
+# Select only the first 10000 rows based on rank
+cleaned_data <- cleaned_data %>%
+  slice(1:10000)
 
 #### Save data ####
 write_parquet(x = cleaned_data, "data/analysis_data/clean_anime.parquet")

### 2024-04-13 paper/paper.qmd
Finished draft of data section

--- 2024-04-12 paper/paper.qmd
@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "My title: still thinking"
+subtitle: "Definitely want a subtitle"
 author: Allen Uy
@@
 
-library(tidyverse)
+library("tidyverse")
+library("arrow")
+library("here")
+library("knitr")
+library("kableExtra")
+
+clean_anime <- read_parquet(here::here("data/analysis_data/clean_anime.parquet"))
 ```
 
-# Introduction
+# Introduction (longer)
 
@@
 
+The estimand of interest is...
+
 We conduct an analysis on the ratings of anime on MAL. Specifically we contrast
+
+The subsequent sections follow a structured format.
+@sec-data outlines the source and variables of interest for our analysis.
+@sec-model details the construction and methodology of the statistical models used.
+@sec-results presents the key findings of our analysis, while @sec-discussion critically reviews the content, addresses the implications of the results, acknowledges model limitations, and suggests potential research directions.
 
@@
 
-The data in this paper is sourced from the MAL API [@MALAPI] and was gathered on April 10, 2024.
+The data in this paper is sourced from the MAL API [@MALAPI] and was gathered on April 12, 2024.
 The rankings of anime in the database are updated twice a day so the data gathered can be assumed to be up to date.
@@
 The user can also give a score to an anime, regardless of status, which is an integer from 1 to 10.
-The score of an anime on MAL is a weighted score calculated as:
+The score of an anime on MAL is a weighted score calculated via the following:
 
 ```{=tex}
-\begin{equation}
+\begin{equation*}
 \text{Weighted Score} = \left( \frac{v}{v + m} \right) \cdot S + \left( \frac{m}{v + m} \right) \cdot C
-\end{equation}
+\end{equation*}
 
@@
 ```
-This equation requires a minimum number of scores to ensures a fair sample size and takes into account popularity and normalizes the score compared to the mean score in the database.
+This equation requires a minimum number of scores to ensure a fair sample size, takes into account popularity, and normalizes the score compared to the mean score in the database.
+Note that for a sufficiently large number of scoring users the weighted score will be close to the actual mean score.
 In addition, MAL verifies whether the user has viewed 1/5 of the series upon completion and excludes scores by illegitimate accounts that try to sway votes.
@@
 Due to the personal nature of these lists we assume that each user and list is associated with exactly one individual.
+
+## Top 10000 Ranked Anime
+
+The MAL API is capable of fetching up to 500 anime based on ranking at a time for a given offset.
+@tbl-anime_dataset shows a small subset of the data gathered.
+Relatively little cleaning was required as the API allows one to specify what fields should be returned.
+The genre was returned as a list of strings which was turned into a multi-hot encoding for data processing.
+MAL has 74 listed genres and themes, so only 2 genre columns are displayed here for readability.
+
+(maybe move this to discussion) Three fields of interest were unable to be retrieved without an API call for a specific id, namely related anime, recommendations, and statistics regarding the exact numbers of member status.
+When attempting to get this data, rate limiting was encountered at roughly 250 calls per 10 minutes, with no clear way to raise the API call limit.
+Due to this the relationships between anime could not investigated thoroughly.
+
+```{r, echo=FALSE}
+#| label: tbl-anime_dataset
+#| tbl-cap: Sample of Anime
+
+bind_rows(head(clean_anime, 3), tail(clean_anime, 3)) |>
+  select(id, title, rank, start_date, studio, mean, popularity, num_list_users,
+         num_scoring_users, adventure, drama) |>
+  kable(
+    booktabs = TRUE,
+    linesep = ""
+  ) |> kable_styling(latex_options = "scale_down")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-score_distribution
+#| fig-cap: Distribution of Scores of Top 10000 Anime
+
+mean_score <- mean(clean_anime$mean)
+
+clean_anime %>%
+  ggplot(aes(x = mean)) +
+  geom_histogram(binwidth = 0.1, color="darkblue", fill="lightblue") +
+  theme_minimal() +
+  geom_vline(aes(xintercept=mean_score), linetype="dashed", size=1) +
+  annotate("text", x = mean_score + 0.1, y = 550, label = paste("Mean Score:", round(mean_score, 2)), 
+           hjust = 0, vjust = -1) +
+  labs(x = "Score", y = "count")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-rank_vs_popularity
+#| fig-cap: Rank vs Popularity for Top 10000 Anime
+
+correlation <- cor(clean_anime$rank, clean_anime$popularity)
+
+clean_anime |>  ggplot(aes(x = rank, y = popularity)) +
+  geom_point(color = "blue", size=0.5, alpha=0.3) +
+  labs(x = "Rank", y = "Popularity") +
+  scale_x_reverse() +
+  scale_y_reverse() +
+  theme_minimal() +
+  geom_vline(xintercept = 5000, color = "black", size=1) +
+  geom_hline(yintercept = 10000, color = "black", size=1) +
+  annotate("text", x = 2500, y = 15000, label = "Hidden Gem", color = "black", size=5, fontface = "bold") +
+  annotate("text", x = 7500, y = 15000, label = "Niche", color = "black", size=5, fontface = "bold") +
+  annotate("text", x = 2500, y = 5000, label = "Top Tier", color = "black", size=5, fontface = "bold") +
+  annotate("text", x = 7500, y = 5000, label = "Classic", color = "black", size=5, fontface = "bold") +
+  geom_smooth(method = "lm", color = "red", se = FALSE)
+  # annotate("text", x = 0, y = -500, label = paste("R:", round(correlation, 2)), 
+  #          hjust = 1, vjust = 0, size = 4, color = "black", fontface = "bold")
+```
+
+From the right skewed distribution of @fig-score_distribution, we observe that it is difficult for an anime to become top rated.
+This makes sense in the context of any subject that is reviewed as it requires a large group of people to consistently find greatness with no glaring flaws.
+It is also sensible that the mean score of the top 10000 anime is closer to 7 than to 5.
+Scores are inherently a subjective opinion and may take into account enjoyability, as well as how 'good' the piece of work is.
+Many people could enjoy a bad show even despite having many flaws.
+This matches the description MAL gives to each score number, where 1 is appalling, 5 is average, 7 is good, and 10 is a masterpiece.
+Seven is often seen as the borderline of acceptable in many contexts (objective source here maybe?).
+
+If scoring is subjective how much of a relationship is there between rating and popularity?
+From @fig-rank_vs_popularity we see there is a moderately strong positive linear correlation between rank and popularity.
+This is also a sensible conclusion as a highly rated anime is more likely to attract new viewers.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-date_vs_popularity
+#| fig-cap: Relationship Between Date and Popularity
+
+ggplot(clean_anime, aes(x = start_date, y = popularity)) +
+  geom_point(color = "blue", size = 0.5, alpha=0.3) +
+  labs(x = "Start Date", y = "Popularity") +
+  theme_minimal() +
+  scale_y_reverse() +
+  geom_smooth(method = "lm", color = "red", se = FALSE)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-date_vs_popularity_modern
+#| fig-cap: Relationship Between Date and Popularity in Modern Anime
+
+modern_anime <- clean_anime |>
+  filter(start_date >= as.Date("2000-01-01"))
+
+ggplot(modern_anime, aes(x = start_date, y = popularity)) +
+  geom_point(color = "blue", size = 0.5, alpha=0.3) +
+  labs(x = "Start Date", y = "Popularity") +
+  theme_minimal() +
+  scale_y_reverse() +
+  geom_smooth(method = "lm", color = "red", se = FALSE)
+```
+
+It may seem like the date an anime airs can be a factor for popularity as older anime could have longer exposure over time or newer anime has more coverage but this does not seem to be the case.
+@fig-date_vs_popularity shows people are less likely to watch very old anime and @fig-date_vs_popularity_modern suggests date is irrelevant to popularity.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-scoring_fraction
+#| fig-cap: Distribution of Scoring Fraction of Top 10000 Anime
+
+mean_fraction <- mean(clean_anime$num_scoring_users / clean_anime$num_list_users)
+
+clean_anime |> ggplot(aes(x=num_scoring_users / num_list_users)) +
+  geom_histogram(binwidth = 0.01, color="darkblue", fill="lightblue") +
+  labs(x = "Fraction of Scoring Users to List Users", y = "Frequency") +
+  annotate("text", x = mean_fraction + 0.1, y = 370, label = paste("Mean Fraction:", round(mean_fraction, 3))) +
+  theme_minimal() +
+  geom_vline(aes(xintercept=mean_fraction), linetype="dashed", size=1)
+```
+
+On average, 39% of users end up rating an anime on their list according to @fig-scoring_fraction.
+There is a strong positive correlation between scoring fraction and popularity, which is sensible as fans of an anime or any media in general are likely express their opinion on that particular media.
+Surprisingly there is a positive correlation between scoring fraction and rank.
+One might expect a normal distribution as people are more likely to voice their opinion on a particularly good or bad piece of work but not so much for average ones.
+Instead we see a linear relationship scoring fraction and rank.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-fraction_relationships
+#| fig-cap: "Correlation to Scoring Fraction"
+#| fig-subcap: ["Popularity plot", "Rank plot"]
+#| layout-ncol: 2
+
+clean_anime |> ggplot(aes(x = num_scoring_users / num_list_users, y = popularity)) +
+  geom_point(color = "blue", size = 0.5, alpha=0.3) +
+  labs(x = "Scoring Fraction", y = "Popularity") +
+  geom_smooth(method = "lm", color = "red", se = FALSE) +
+  theme_minimal() +
+  scale_y_reverse()
+
+clean_anime |> ggplot(aes(x = num_scoring_users / num_list_users, y = rank)) +
+  geom_point(color = "blue", size = 0.5, alpha=0.3) +
+  labs(x = "Scoring Fraction", y = "Rank") +
+  geom_smooth(method = "lm", color = "red", se = FALSE) +
+  theme_minimal() +
+  scale_y_reverse()
+```
 
@@
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
 ```
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
+# pp_check(first_model) +
+#   theme_classic() +
+#   theme(legend.position = "bottom")
+# 
+# posterior_vs_prior(first_model) +
+#   theme_minimal() +
+#   scale_color_brewer(palette = "Set1") +
+#   theme(legend.position = "bottom") +
+#   coord_flip()
 ```
@@
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
+# plot(first_model, "trace")
+# 
+# plot(first_model, "rhat")
 ```

### 2024-04-13 paper/paper.qmd
Updated LLM usage

@@
 
+### Score Distribution (is there such thing as too many sections?)
+
 From the right skewed distribution of @fig-score_distribution, we observe that it is difficult for an anime to become top rated.
@@
 Seven is often seen as the borderline of acceptable in many contexts (objective source here maybe?).
+
+### Rank and Popularity
 
@@
 
+### Date and Popularity
+
 It may seem like the date an anime airs can be a factor for popularity as older anime could have longer exposure over time or newer anime has more coverage but this does not seem to be the case.
@@
 
+### Scoring Fraction
+
 On average, 39% of users end up rating an anime on their list according to @fig-scoring_fraction.
-There is a strong positive correlation between scoring fraction and popularity, which is sensible as fans of an anime or any media in general are likely express their opinion on that particular media.
-Surprisingly there is a positive correlation between scoring fraction and rank.
+There is a strong positive correlation between scoring fraction and popularity as seen in @fig-fraction_relationships-1, which is sensible as fans of an anime or any media in general are likely express their opinion on that particular media.
+Surprisingly in @fig-fraction_relationships-2 there is a positive correlation between scoring fraction and rank.
 One might expect a normal distribution as people are more likely to voice their opinion on a particularly good or bad piece of work but not so much for average ones.
@@
 ```
+
+TODO look at studio and genre
 

### 2024-04-14 paper/paper.qmd
Added datasheet

@@
 
+Keep member distribution?
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-member_distribution
+#| fig-cap: Distribution of Members of Top 10000 Anime
+
+mean_members <- mean(clean_anime$num_list_users)
+
+clean_anime %>%
+  ggplot(aes(x = num_list_users)) +
+  geom_histogram(binwidth=50000, color="darkblue", fill="lightblue") +
+  theme_minimal() +
+  geom_vline(aes(xintercept=mean_members), linetype="dashed", size=1) +
+  annotate("text", x = mean_members + 0.1, y = 550, label = paste("Mean Members", round(mean_members, 2)), 
+           hjust = 0, vjust = -1) +
+  labs(x = "Members", y = "count")
+```
+
 # Model

### 2024-04-14 paper/paper.qmd
Finished draft of model and results

--- 2024-04-13 paper/paper.qmd
@@
 ---
-title: "My title: still thinking"
-subtitle: "Definitely want a subtitle"
+title: "Animazing"
+subtitle: "What was found"
 author: Allen Uy
@@
   select(id, title, rank, start_date, studio, mean, popularity, num_list_users,
-         num_scoring_users, adventure, drama) |>
+         num_scoring_users, adventure, drama, fraction, days_since_start) |>
   kable(
@@
 
-### Score Distribution (is there such thing as too many sections?)
+### Score Distribution {#sec-score-distribution}
 
@@
 
-### Rank and Popularity
+### Rank and Popularity {#sec-rank-and-popularity}
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#| label: fig-date_vs_popularity
-#| fig-cap: Relationship Between Date and Popularity
+#| label: fig-date_relationships
+#| fig-cap: "Correlation to Date"
+#| fig-subcap: ["Popularity plot", "Rank plot"]
+#| layout-ncol: 2
 
@@
   geom_smooth(method = "lm", color = "red", se = FALSE)
+
+ggplot(clean_anime, aes(x = start_date, y = rank)) +
+  geom_point(color = "blue", size = 0.5, alpha=0.3) +
+  labs(x = "Start Date", y = "Rank") +
+  theme_minimal() +
+  scale_y_reverse() +
+  geom_smooth(method = "lm", color = "red", se = FALSE)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#| label: fig-date_vs_popularity_modern
-#| fig-cap: Relationship Between Date and Popularity in Modern Anime
+#| label: fig-date_relationships_modern
+#| fig-cap: "Correlation to Modern Dates"
+#| fig-subcap: ["Popularity plot", "Rank plot"]
+#| layout-ncol: 2
 
@@
   geom_smooth(method = "lm", color = "red", se = FALSE)
+
+ggplot(modern_anime, aes(x = start_date, y = rank)) +
+  geom_point(color = "blue", size = 0.5, alpha=0.3) +
+  labs(x = "Start Date", y = "Rank") +
+  theme_minimal() +
+  scale_y_reverse() +
+  geom_smooth(method = "lm", color = "red", se = FALSE)
 ```
 
-### Date and Popularity
+### Correlation to Date {#sec-correlation-to-date}
 
 It may seem like the date an anime airs can be a factor for popularity as older anime could have longer exposure over time or newer anime has more coverage but this does not seem to be the case.
-@fig-date_vs_popularity shows people are less likely to watch very old anime and @fig-date_vs_popularity_modern suggests date is irrelevant to popularity.
+@fig-date_relationships-1 shows people are less likely to watch very old anime and @fig-date_relationships_modern-1 suggests date is generally irrelevant to popularity but modern anime does have more viewership compared to older anime by the density of the points.
+
+We observe a weaker relationship between date and rating in @fig-date_relationships-2 which suggests viewers are still appreciative of older works.
+As the amount of anime produced has increased in modern times, @fig-date_relationships_modern-2 suggests that for every 'good' anime there is a 'bad' anime to match it.
 
@@
 
-mean_fraction <- mean(clean_anime$num_scoring_users / clean_anime$num_list_users)
+mean_fraction <- mean(clean_anime$fraction)
 
-clean_anime |> ggplot(aes(x=num_scoring_users / num_list_users)) +
+clean_anime |> ggplot(aes(x=fraction)) +
   geom_histogram(binwidth = 0.01, color="darkblue", fill="lightblue") +
   labs(x = "Fraction of Scoring Users to List Users", y = "Frequency") +
-  annotate("text", x = mean_fraction + 0.1, y = 370, label = paste("Mean Fraction:", round(mean_fraction, 3))) +
+  annotate("text", x = mean_fraction + 0.3, y = 370, label = paste("Mean Fraction:", round(mean_fraction, 3))) +
   theme_minimal() +
@@
 
-### Scoring Fraction
+### Scoring Fraction {#sec-scoring-fraction}
 
@@
 One might expect a normal distribution as people are more likely to voice their opinion on a particularly good or bad piece of work but not so much for average ones.
-Instead we see a linear relationship scoring fraction and rank.
+Instead we see a linear relationship between scoring fraction and rank.
 
@@
 
-clean_anime |> ggplot(aes(x = num_scoring_users / num_list_users, y = popularity)) +
+clean_anime |> ggplot(aes(x = fraction, y = popularity)) +
   geom_point(color = "blue", size = 0.5, alpha=0.3) +
@@
 
-clean_anime |> ggplot(aes(x = num_scoring_users / num_list_users, y = rank)) +
+clean_anime |> ggplot(aes(x = fraction, y = rank)) +
   geom_point(color = "blue", size = 0.5, alpha=0.3) +
@@
 
-TODO look at studio and genre
+# Model {#sec-model}
 
-# Model
+Here we briefly describe the Bayesian analysis model used to investigate the user score of anime on MAL. Background details and diagnostics are included in [Appendix -@sec-model-details].
 
-The goal of our modelling strategy is twofold. Firstly,...
+## Model Set-up
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+From the preliminary analysis conducted in @sec-data, we build a multiple linear regression model to predict the rating of an anime based on quantitative statistics.
+Define $y_i$ as the user score of the anime $i$.
+Then $\text{fraction}_i$ is the fraction of users who have rated the anime $i$ to members of the anime $i$, $\text{popularity}_i$ is the total members of anime $i$, and $\text{startDate}_i$ is the number of days from the start date of anime $i$ to the current date.
 
@@
 y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+\mu_i &= \beta_0 + \beta_1 \times \text{fraction} + \beta_2 \times \text{popularity} + \beta_3 \times \text{startDate}\\
+\beta_0 &\sim \mbox{Normal}(0, 1.6) \\
+\beta_1 &\sim \mbox{Normal}(0, 13) \\
+\beta_2 &\sim \mbox{Normal}(0, 3.6 \times 10^{-4}) \\
+\beta_3 &\sim \mbox{Normal}(0, 6.3 \times 10^{-6}) \\
+\sigma &\sim \mbox{Exponential}(1.6)
 \end{align}
 ```
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm. We use the default priors from `rstanarm` which are Normal distributions and apply autoscaling for better results.
 
-### Model justification
+### Model Justification
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We expect a positive relationship between the score of the anime and scoring fraction as seen in @sec-scoring-fraction.
+This is likely to be the most important factor in our model.
+We expect a very minor to no relationship between the score of the anime and the start date of an anime as seen in @sec-correlation-to-date.
+As such this coefficient is expected to be close to zero.
+Finally, we expect a minor positive relationship between the score of an anime and its popularity as seen in @sec-rank-and-popularity.
+This coefficient will likely be close to zero and smaller than start date, as an anime can have millions of members, but should be a better indicator than start date.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
+# Results {#sec-results}
 
 Our results are summarized in @tbl-modelresults.
+Our model observes a score intercept of 6.02, which means when an anime has been out for 0 days, has 0 members and thus 0 scoring fraction, it will likely have a user score of 6.34.
+This is slightly nonsensical as an anime had to have a positive scoring fraction and the minimum amount of scoring users to be ranked within the top 10000.
+When considering only the mean scoring fraction in @sec-scoring-fraction of 0.39, our model predicts a user score of $6.34 + 1.55\times0.39=6.94$, which is close to the mean user score of 6.91 seen in @sec-score-distribution.
+The start date coefficient is extremely small indicating the date of an anime has no impact on its score.
+For a 10 year old anime the model expects the score to decrease by $-1.605 \times 10^{-5} \times (10 \times 365)=-0.06$, which can be considered a neglible amount.
+Finally, for every 1 million members of an anime, its score increases by $7.77 \times 10^{-7}\times10^6=0.78$ .
 
@@
 
-library(rstanarm)
-
+library("rstanarm")
+model <- readRDS(here::here("models/model.rds"))
 ```
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Explanatory models of score based on scoring fraction, popularity, and start date"
 #| warning: false
 
+library("modelsummary")
+
+my_fmt <- list(
+  intercept = list(fmt = "%.2f"),
+  fraction = list(fmt = "%.2f"),
+  days_since_start = list(fmt = "%#.2e"),
+  num_list_users = list(fmt = "%#.2e")
+)
+
+table <- modelsummary(
+  model,
+  statistic = "mad",
+  fmt = my_fmt,
+  output = "kableExtra"
+)
+
+table |> kable_styling(latex_options = "scale_down")
 ```
 
-# Discussion
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelpredictions
+#| tbl-cap: "Comparing predictions of model to actual scores"
+#| warning: false
+
+predictions <- clean_anime |>
+  filter(!is.na(fraction) & !is.na(num_list_users) & !is.na(days_since_start)) |>
+  mutate(predicted = predict(model, .)) |>
+  select(title, rank, popularity, mean, num_list_users, fraction, start_date, days_since_start, predicted)
+
+bind_rows(head(predictions, 5), tail(predictions, 5)) |>
+  select(id, title, rank, start_date, studio, mean, popularity, num_list_users,
+         num_scoring_users, adventure, drama, fraction, days_since_start) |>
+  kable(
+    booktabs = TRUE,
+    linesep = ""
+  ) |> kable_styling(latex_options = "scale_down")
+```
+
+@tbl-modelpredictions shows the predictions of our model compared to the actual scores of the top 5 and bottom 5 anime in the dataset. Some observations that should be noted are:
+
+1.  The score intercept is higher than the score of lower ranked anime
+2.  The model is harsh on highly ranked anime that are not yet popular
+
+# Discussion {#sec-discussion}
 
@@
 
-# pp_check(first_model) +
-#   theme_classic() +
-#   theme(legend.position = "bottom")
-# 
-# posterior_vs_prior(first_model) +
-#   theme_minimal() +
-#   scale_color_brewer(palette = "Set1") +
-#   theme(legend.position = "bottom") +
-#   coord_flip()
+# analysis_data <- clean_anime
+
+pp_check(model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
 ```

### 2024-04-14 scripts/02-data_cleaning.R

@@ -7,11 +7,14 @@
 # License: MIT
 # Pre-requisites: 01a-download_data is run and raw data is saved in 
 # appropriate location
+# Update ref_date as needed
 
 #### Workspace setup ####
 library("tidyverse")
 library("arrow")
 library("janitor")
+
+ref_date = as.Date("2024-04-12")
 
 
 #### Clean data ####
@@ -39,6 +42,11 @@ cleaned_data$start_date <- as.Date(cleaned_data$start_date)
 cleaned_data$num_scoring_users <- as.integer(cleaned_data$num_scoring_users)
 cleaned_data$num_list_users <- as.integer(cleaned_data$num_list_users)
 
+cleaned_data<- cleaned_data |>
+  mutate(days_since_start = as.integer(ref_date - start_date))
+
+cleaned_data <- cleaned_data |>
+  mutate(fraction = num_scoring_users / num_list_users)
 
 cleaned_data <- cleaned_data |> select(-genres) |>
   clean_names()

### 2024-04-14 scripts/04-model.R

@@ -1,37 +1,44 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models 
+# Author: Allen Uy
+# Date: 13 April 2024
+# Contact: allen.uy@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-data_cleaning is run and analysis data is placed in
+# appropriate location
 
 
 #### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
+library("tidyverse")
+library("rstanarm")
+library("modelsummary")
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+clean_anime <- read_parquet("data/analysis_data/clean_anime.parquet")
 
 ### Model data ####
-first_model <-
+model <-
   stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
+    formula = mean ~ fraction + days_since_start + num_list_users,
+    data = clean_anime,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
+    seed = 42
   )
+
+summary(model)
+
+coef(model)
+
+prior_summary(model)
 
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  model,
+  file = "models/model.rds"
 )
 
 

### 2024-04-14 paper/paper.qmd
Minor improvements. Abstract and title draft.

@@
 ---
-title: "Animazing"
-subtitle: "What was found"
+title: "Predicting which anime are animazing through quantitative analysis"
+subtitle: "People are more likely to rate great anime, regardless of age"
 author: Allen Uy
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper examines the top 10000 anime on MyAnimeList (MAL) by user score to understand the tendencies of highly rated anime.
+Using data provided by the MAL API, we discovered that the fraction of users that rate an anime to the total users that have engaged with the anime is a large indicator of user score.
+Our multiple linear regression model predicts the user score of an anime based on scoring fraction, date, and popularity and may indicate highly rated anime that have not yet gotten adequate exposure based on difference between the predicted and actual scores.
+This concept of scoring fraction is applicable to media forms beyond anime and may serve as the basis for recommendation algorithms."
 format: pdf
@@
 bibliography: references.bib
+keywords: anime, regression, MyAnimeList
 ---
@@
 Anime refers to animation originating from Japan.
+(I want to introduce what anime is better).
 In 2021, half of Netflix's 222 million subscribers watched some anime on the platform and viewership saw an increase of 20% in the total hours over the previous year [@netflixAnime].
+Anime is not much different compared to other forms of media, however anime and animation in general is still often regarded by many as 'childish', despite plenty of anime covering serious topics[@enjoyAnimation].
 
-MyAnimeList, herein referred to as MAL, is one of the largest and most popular anime database and communities online.
-Users are able to keep track of anime they have watched or plan to, as well as rate and find similar anime.
+MyAnimeList, herein referred to as MAL, is one of the largest and most popular anime databases and communities online.
+Users are able to keep track of anime they have watched or plan to watch, as well as rate and find similar anime.
+MAL is similar to IMDb in terms of functionality.
 
-The estimand of interest is...
+The estimand of interest is the effect of
 
@@
 MAL has 74 listed genres and themes, so only 2 genre columns are displayed here for readability.
+The fraction column was calculated as the fraction of num_scoring_users to num_list_users, this is the fraction of users that gave a score to the anime.
+The days_since_start column was calculated as the integer day difference between the start date of the anime and the date the dataset was gathered.
 
@@
 
-# analysis_data <- clean_anime
-
 pp_check(model) +
@@
 ## Diagnostics
+
+Maybe don't keep this
 
@@
 
+# Datasheet
+
+Link to datasheet in repo here
+
+# R package
+
+TODO: create package
+
 \newpage

### 2024-04-14 paper/paper.qmd
Rendered paper

@@
 bibliography: references.bib
-keywords: anime, regression, MyAnimeList
 ---
@@
 ```
+
+Can I add keywords under abstract somehow? keywords: anime, regression, MyAnimeList
 
@@
 
-my_fmt <- list(
-  intercept = list(fmt = "%.2f"),
-  fraction = list(fmt = "%.2f"),
-  days_since_start = list(fmt = "%#.2e"),
-  num_list_users = list(fmt = "%#.2e")
-)
-
 table <- modelsummary(
@@
   statistic = "mad",
-  fmt = my_fmt,
+  fmt = fmt_sprintf("%.3e"),
   output = "kableExtra"
@@
   mutate(predicted = predict(model, .)) |>
-  select(title, rank, popularity, mean, num_list_users, fraction, start_date, days_since_start, predicted)
+  select(title, rank, popularity, num_list_users, fraction, start_date, days_since_start, mean, predicted)
 
 bind_rows(head(predictions, 5), tail(predictions, 5)) |>
-  select(id, title, rank, start_date, studio, mean, popularity, num_list_users,
-         num_scoring_users, adventure, drama, fraction, days_since_start) |>
   kable(

### 2024-04-14 paper/paper.qmd
Updated model justification

@@
 \mu_i &= \beta_0 + \beta_1 \times \text{fraction} + \beta_2 \times \text{popularity} + \beta_3 \times \text{startDate}\\
-\beta_0 &\sim \mbox{Normal}(0, 1.6) \\
-\beta_1 &\sim \mbox{Normal}(0, 13) \\
+\beta_0 &\sim \mbox{Normal}(7, 1.6) \\
+\beta_1 &\sim \mbox{Normal}(1, 13) \\
 \beta_2 &\sim \mbox{Normal}(0, 3.6 \times 10^{-4}) \\
@@
 ```
-We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm. We use the default priors from `rstanarm` which are Normal distributions and apply autoscaling for better results.
+We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm.
+We use Normal priors for the coefficients centered around sensible values which are detailed in the following section.
+We apply autoscaling in `rstanarm` as we are unsure of the likely range of these coefficients.
 
@@
 
+We expect the intercept of the model to be close to the mean score of anime so we center the prior distribution around it.
 We expect a positive relationship between the score of the anime and scoring fraction as seen in @sec-scoring-fraction.
-This is likely to be the most important factor in our model.
+This is likely to be the most important factor in our model and since the parameter is a fraction its coefficient should be relatively large, which is why we chose to center around 1.
 We expect a very minor to no relationship between the score of the anime and the start date of an anime as seen in @sec-correlation-to-date.

### 2024-04-14 scripts/04-model.R

@@ -22,8 +22,8 @@ model <-
     formula = mean ~ fraction + days_since_start + num_list_users,
     data = clean_anime,
     family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior = normal(location = c(1,0,0), scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 7, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 42
   )

### 2024-04-15 paper/paper.qmd
Finished draft of discussion. Intro WIP.

@@
 
-Can I add keywords under abstract somehow? keywords: anime, regression, MyAnimeList
+Keywords: anime, regression, MyAnimeList, scoring fraction, rank, popularity, rating
 
@@
 The MAL API is capable of fetching up to 500 anime based on ranking at a time for a given offset.
-@tbl-anime_dataset shows a small subset of the data gathered.
+@tbl-anime_dataset shows a small subset of the data gathered along with the main variables of interest.
 Relatively little cleaning was required as the API allows one to specify what fields should be returned.
-The genre was returned as a list of strings which was turned into a multi-hot encoding for data processing.
-MAL has 74 listed genres and themes, so only 2 genre columns are displayed here for readability.
+The genre was returned as a JSON array which was turned into a multi-hot encoding for data processing.
 The fraction column was calculated as the fraction of num_scoring_users to num_list_users, this is the fraction of users that gave a score to the anime.
 The days_since_start column was calculated as the integer day difference between the start date of the anime and the date the dataset was gathered.
-
-(maybe move this to discussion) Three fields of interest were unable to be retrieved without an API call for a specific id, namely related anime, recommendations, and statistics regarding the exact numbers of member status.
-When attempting to get this data, rate limiting was encountered at roughly 250 calls per 10 minutes, with no clear way to raise the API call limit.
-Due to this the relationships between anime could not investigated thoroughly.
 
@@
 bind_rows(head(clean_anime, 3), tail(clean_anime, 3)) |>
-  select(id, title, rank, start_date, studio, mean, popularity, num_list_users,
-         num_scoring_users, adventure, drama, fraction, days_since_start) |>
+  select(id, title, rank, start_date, mean, popularity, num_list_users,
+         num_scoring_users, fraction, days_since_start) |>
   kable(
@@
 ```
+
+### Score Distribution {#sec-score-distribution}
+
+From the right skewed distribution of @fig-score_distribution, we observe that it is difficult for an anime to become top rated.
+This makes sense in the context of any subject that is reviewed as it requires a large group of people to consistently find greatness with no glaring flaws.
+It is also sensible that the mean score of the top 10000 anime is closer to 7 than to 5.
+Scores are inherently a subjective opinion and may take into account enjoyability, as well as how 'good' the piece of work is.
+Many people could enjoy a bad show even despite having many flaws.
+This matches the description MAL gives to each score number, where 1 is appalling, 5 is average, 7 is good, and 10 is a masterpiece.
+Seven is often seen as the average review score according to this forum discussion (see @averageScore).
 
@@
 
+### Rank and Popularity {#sec-rank-and-popularity}
+
+If scoring is subjective how much of a relationship is there between rating and popularity?
+From @fig-rank_vs_popularity we see there is a moderately strong positive linear correlation between rank and popularity.
+This is also a sensible conclusion as a highly rated anime is more likely to attract new viewers.
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
   theme_minimal() +
-  geom_vline(xintercept = 5000, color = "black", size=1) +
-  geom_hline(yintercept = 10000, color = "black", size=1) +
-  annotate("text", x = 2500, y = 15000, label = "Hidden Gem", color = "black", size=5, fontface = "bold") +
-  annotate("text", x = 7500, y = 15000, label = "Niche", color = "black", size=5, fontface = "bold") +
-  annotate("text", x = 2500, y = 5000, label = "Top Tier", color = "black", size=5, fontface = "bold") +
-  annotate("text", x = 7500, y = 5000, label = "Classic", color = "black", size=5, fontface = "bold") +
+  # geom_vline(xintercept = 5000, color = "black", size=1) +
+  # geom_hline(yintercept = 10000, color = "black", size=1) +
+  # annotate("text", x = 2500, y = 15000, label = "Hidden Gem", color = "black", size=5, fontface = "bold") +
+  # annotate("text", x = 7500, y = 15000, label = "Niche", color = "black", size=5, fontface = "bold") +
+  # annotate("text", x = 2500, y = 5000, label = "Top Tier", color = "black", size=5, fontface = "bold") +
+  # annotate("text", x = 7500, y = 5000, label = "Classic", color = "black", size=5, fontface = "bold") +
   geom_smooth(method = "lm", color = "red", se = FALSE)
-  # annotate("text", x = 0, y = -500, label = paste("R:", round(correlation, 2)), 
-  #          hjust = 1, vjust = 0, size = 4, color = "black", fontface = "bold")
 ```
 
-### Score Distribution {#sec-score-distribution}
+### Correlation to Date {#sec-correlation-to-date}
 
-From the right skewed distribution of @fig-score_distribution, we observe that it is difficult for an anime to become top rated.
-This makes sense in the context of any subject that is reviewed as it requires a large group of people to consistently find greatness with no glaring flaws.
-It is also sensible that the mean score of the top 10000 anime is closer to 7 than to 5.
-Scores are inherently a subjective opinion and may take into account enjoyability, as well as how 'good' the piece of work is.
-Many people could enjoy a bad show even despite having many flaws.
-This matches the description MAL gives to each score number, where 1 is appalling, 5 is average, 7 is good, and 10 is a masterpiece.
-Seven is often seen as the borderline of acceptable in many contexts (objective source here maybe?).
-
-### Rank and Popularity {#sec-rank-and-popularity}
-
-If scoring is subjective how much of a relationship is there between rating and popularity?
-From @fig-rank_vs_popularity we see there is a moderately strong positive linear correlation between rank and popularity.
-This is also a sensible conclusion as a highly rated anime is more likely to attract new viewers.
+It may seem like the date an anime airs can be a factor for popularity as older anime could have longer exposure over time or newer anime has more coverage but this does not seem to be the case.
+@fig-date_relationships-1 shows people are less likely to watch very old anime and @fig-date_relationships_modern-1 suggests date is generally irrelevant to popularity but modern anime does have more viewership compared to older anime by the density of the points.
 
@@
 ```
+
+We observe a weaker relationship between date and rating in @fig-date_relationships-2 which suggests viewers are still appreciative of older works.
+As the amount of anime produced has increased in modern times, @fig-date_relationships_modern-2 suggests that for every 'good' anime there is a 'bad' anime to match it.
 
@@
 
-### Correlation to Date {#sec-correlation-to-date}
+### Scoring Fraction {#sec-scoring-fraction}
 
-It may seem like the date an anime airs can be a factor for popularity as older anime could have longer exposure over time or newer anime has more coverage but this does not seem to be the case.
-@fig-date_relationships-1 shows people are less likely to watch very old anime and @fig-date_relationships_modern-1 suggests date is generally irrelevant to popularity but modern anime does have more viewership compared to older anime by the density of the points.
-
-We observe a weaker relationship between date and rating in @fig-date_relationships-2 which suggests viewers are still appreciative of older works.
-As the amount of anime produced has increased in modern times, @fig-date_relationships_modern-2 suggests that for every 'good' anime there is a 'bad' anime to match it.
+On average, 39% of users end up rating an anime on their list according to @fig-scoring_fraction.
+There is a strong positive correlation between scoring fraction and popularity as seen in @fig-fraction_relationships-1, which is sensible as fans of an anime or any media in general are likely express their opinion on that particular media.
+Surprisingly in @fig-fraction_relationships-2 there is a positive linear correlation between scoring fraction and rank.
+One might expect a normal distribution as people are more likely to voice their opinion on a particularly good or bad piece of work but not so much for average ones.
+Instead we see a linear relationship between scoring fraction and rank.
 
@@
   labs(x = "Fraction of Scoring Users to List Users", y = "Frequency") +
-  annotate("text", x = mean_fraction + 0.3, y = 370, label = paste("Mean Fraction:", round(mean_fraction, 3))) +
+  annotate("text", x = mean_fraction + 0.15, y = 370, label = paste("Mean Fraction:", round(mean_fraction, 3))) +
   theme_minimal() +
@@
 ```
-
-### Scoring Fraction {#sec-scoring-fraction}
-
-On average, 39% of users end up rating an anime on their list according to @fig-scoring_fraction.
-There is a strong positive correlation between scoring fraction and popularity as seen in @fig-fraction_relationships-1, which is sensible as fans of an anime or any media in general are likely express their opinion on that particular media.
-Surprisingly in @fig-fraction_relationships-2 there is a positive correlation between scoring fraction and rank.
-One might expect a normal distribution as people are more likely to voice their opinion on a particularly good or bad piece of work but not so much for average ones.
-Instead we see a linear relationship between scoring fraction and rank.
 
@@
 ```{=tex}
-\begin{align} 
+\begin{align*} 
 y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
@@
 \sigma &\sim \mbox{Exponential}(1.6)
-\end{align}
+\end{align*}
 ```
@@
 This is slightly nonsensical as an anime had to have a positive scoring fraction and the minimum amount of scoring users to be ranked within the top 10000.
-When considering only the mean scoring fraction in @sec-scoring-fraction of 0.39, our model predicts a user score of $6.34 + 1.55\times0.39=6.94$, which is close to the mean user score of 6.91 seen in @sec-score-distribution.
+When considering only the mean scoring fraction in @sec-scoring-fraction of 0.39, our model predicts a user score of $6.34 + 1.546\times0.39=6.94$, which is close to the mean user score of 6.91 seen in @sec-score-distribution.
 The start date coefficient is extremely small indicating the date of an anime has no impact on its score.
-For a 10 year old anime the model expects the score to decrease by $-1.605 \times 10^{-5} \times (10 \times 365)=-0.06$, which can be considered a neglible amount.
-Finally, for every 1 million members of an anime, its score increases by $7.77 \times 10^{-7}\times10^6=0.78$ .
+For a 10 year old anime the model expects the score to decrease by $-1.605 \times 10^{-5} \times (10 \times 365)=-0.06$, which can be considered a negligible amount.
+Finally, for every 1 million members of an anime, its score increases by $7.776 \times 10^{-7}\times10^6=0.78$.
+
+Our model has an R2 of 0.276 meaning 27.6% of variance in user score is explained by effectively only scoring fraction and popularity, as only the oldest anime are affected by the start date coefficient.
+This is relatively impressive, considering the subjective nature of reviews, that user score can possibly be predicted purely by numbers.
 
@@
 
-table |> kable_styling(latex_options = "scale_down")
+# table |> kable_styling(latex_options = "scale_down")
+table
 ```
+
+@tbl-modelpredictions shows the predictions of our model compared to the actual scores of the top 5 and bottom 5 anime in the dataset. Some observations that should be noted are:
+
+1.  The score intercept is higher than the score of lower ranked anime
+2.  The model is harsh on highly ranked anime that are not yet popular
 
@@
 
-@tbl-modelpredictions shows the predictions of our model compared to the actual scores of the top 5 and bottom 5 anime in the dataset. Some observations that should be noted are:
-
-1.  The score intercept is higher than the score of lower ranked anime
-2.  The model is harsh on highly ranked anime that are not yet popular
-
 # Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+## Key Findings {#sec-first-point}
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+From the visualizations in @sec-data we discover 3 key findings:
 
-## Second discussion point
+1.  There exists a positive relationship between rank and popularity.
+2.  Except for the oldest anime, anime is popular regardless of age.
+3.  The fraction of people that score an anime to the total members of an anime is a strong indicatowwwwwwwwwr of rating.
 
-## Third discussion point
+Through a multiple linear regression model built in @sec-model, we find that the base anime is given a score of 6.34.
+Every percentage point in the scoring fraction improves the score by 0.01546.
+For every day an anime has been released its score decreases by $-1.605\times10^{-5}$, which is only relevant for the oldest anime on the database.
+For every 1 million members of an anime its score increases by 0.7776.
 
-## Weaknesses and next steps
+The correlation found in @sec-scoring-fraction is surprising as it is contrary to human psychology.
+People are more likely to remember negative experiences so one might expect an increase in scoring fraction for low quality anime @negativeExperience.
+However we find the opposite on MAL, suggesting people are less likely to rate low quality anime, perhaps as a way to forget about the show.
 
-Weaknesses and next steps should also be included.
+## Applications
+
+When comparing the predicted scores of the model and the actual user scores on MAL we notice that the model performs poorly for highly rated but not yet popular anime in terms of total member count.
+This matches the rank-popularity relation discussed in @sec-rank-and-popularity.
+This observation leads to the potential usage of the model as an indicator of which anime are not popular enough relative to their ranking.
+
+For instance, if we look at Sousou no Frieren in @tbl-modelresults we see it is by far the highest rated anime on MAL.
+One could assume that the main reason the anime is not yet popular in terms of total member count is due to airing only recently.
+The difference between the predicted score and the actual score can indicate an anime should get more viewership relative to its quality.
+This scoring could be used in a recommendation system to highlight anime that may be deserving of viewership.
+
+## Weaknesses and Next steps
+
+There is some noise regarding the relationship between rating and popularity.
+How much of popularity is due to rating and how much of rating is due to popularity are areas of interest.
+We assume that each user on MAL is a unique individual due to the personal nature of lists.
+It would not generally serve much purpose for a person to keep track of separate lists.
+However in the past there have been issues of people attempting to artificially lower or raise the scores of some anime @MALBrigading.
+Since then MAL has attempted to police this issue and we do not believe it should be a concern in this dataset.
+
+Three fields of interest were unable to be retrieved without an API call for a specific id, namely related anime, recommendations, and statistics regarding the exact numbers of member status.
+When attempting to get this data, rate limiting was encountered at roughly 250 calls per 10 minutes, with no clear way to raise the API call limit.
+Due to this the relationships between anime could not investigated thoroughly.
+Analysis of a graph structure could prove interesting, especially in the context of recommendations and series of anime.
+
+A variable that would likely be helpful in our model is drop rate, which can be calculated as the fraction of users that label an anime as dropped compared to the total members of that anime.
+As mentioned previously this variable is capable of being retrieved from the API but would take a long time to gather.
+We believe that higher ranked anime are likely to correspond to lower drop rate.
+
+An analysis on scoring fraction should be done on IMDb if applicable to verify whether the assumptions made in this paper apply to other forms of media beyond anime.
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
+This compares the actual scores of anime with simulations from the posterior distribution.
+The solid black line is the score distribution seen in @sec-score-distribution and we see that the model fits the data relatively well for only being capable of making a normally distributed posterior.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
+This show how much the estimates change once data are taken into account.
+We see that the posterior coefficients are close the prior, indicating a good choice of priors.
 
@@
 
-Maybe don't keep this
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-stanareyouokay-1 and @fig-stanareyouokay-2 are trace and Rhat plots of our model.
+We see horizontal lines that bounce around and have overlap between the chains in the trace plot and values close to 1 in the Rhat plot.
+This suggests our model ran into no problems.
 
@@
 
-# plot(first_model, "trace")
-# 
-# plot(first_model, "rhat")
+plot(model, "trace")
+
+plot(model, "rhat")
 ```

### 2024-04-17 scripts/00-simulate_data.R
Updated README and added copy of LLM transcript

@@ -13,7 +13,7 @@ set.seed(42)
 
 
 #### Simulate data ####
-num_obs <- 100
+num_obs <- 1000
 start_date <- as.Date("2000-01-01")
 end_date <- as.Date("2024-04-10")
 num_days <- end_date - start_date
@@ -29,7 +29,8 @@ data <- tibble(
   rank = rank(-score),
   genre = random_genres,
   members = round(runif(num_obs, 100, 1000000)),
-  popularity = rank(-members)
+  popularity = rank(-members),
+  fraction = pmin(pmax(rnorm(num_obs, mean=0.39, sd=0.1), 0), 1)
 )
 
 score_distribution_plot <- ggplot(data, aes(x = score)) +
@@ -51,5 +52,12 @@ rank_popularity_plot <- ggplot(data, aes(x = rank, y = popularity)) +
   theme_minimal()
 
 rank_popularity_plot
+
+fraction_distribution_plot <- data |> ggplot(aes(x=fraction)) +
+  geom_histogram(binwidth = 0.01, color="darkblue", fill="lightblue") +
+  labs(x = "Fraction of Scoring Users to List Users", y = "Frequency") +
+  theme_minimal()
+
+fraction_distribution_plot
 
 

### 2024-04-18 other/datasheet/datasheet.qmd
Linted and styled scripts

---
title: "Datasheet for 'Top 10000 Ranked Anime on MyAnimeList'"
author: Allen Uy
thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of popularity and quality in anime listed on MyAnimeList (MAL). All the data is publicly available through their website but there is no easy way to access a large quantity of this information without their API.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The data was collected by Allen Uy, an undergraduate student at the University of Toronto and the author of this paper.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - N/A
4. *Any other comments?*
    - N/A

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each row in the dataset represents an anime within the top 10000 of MAL by user rating. An anime could be a different media type such as TV or movie but this information was not used in this analysis. The API can retrieve the media_type if needed.
2. *How many instances are there in total (of each type, if appropriate)?*
	- N/A
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a subset of all anime contained on MAL. At the time of writing there was approximately 14000 ranked anime with many more in the database. The dataset contains the anime ranked 1-10000 at the time of writing.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance contains the cleaned features of anime such as id, title, start date, studio, genre, etc.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- N/A
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- A few anime may not have a start date or studio listed as this information is unknown.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Relationships are not listed in this dataset. It is possible to obtain related anime based on an API call using the anime id.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- N/A
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Testing of the cleaned dataset indicated uniqueness and only missing values for previously mentioned attributes.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No
16. *Any other comments?*
	- None

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was gathered on April 12, 2024 via the MAL API, specifically using the `/anime/ranking` endpoint. The JSON object was read into R.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The `httr2` library was used to make the API calls.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The top 10000 ranked anime were chosen for analysis.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Users of MAL who scored and added anime to their listed contributed to statistics of the anime. Only the author was involved in the data collection process.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data reflects the MAL database as of April 12, 2024.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- N/A
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was obtained via the MAL API.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- An API key was registed with MAL with a description of intention of usage.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Users contribute to statistics on MAL as per the ToS.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Users are capable of deleting their account.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- N/A
12. *Any other comments?*
	- None

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- The genres of an anime were returned as a JSON object. The unique genres returned by this were converted to columns and assigned boolean values of 0 and 1.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data is contained in `data/raw_data/anime_rankings`
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- All scripts used in analysis are contained in this repo under `scripts`.
4. *Any other comments?*
	- None

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- No this dataset was created for the purpose of this paper
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- N/A
3. *What (other) tasks could the dataset be used for?*
	- The dataset could be used for many other tasks. Many other relationships between the attributes can be explored.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- N/A
6. *Any other comments?*
	- None

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Not explicity. Third parties are welcome to use this data.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- An R package to easily generate the data is planned to be created.
3. *When will the dataset be distributed?*
	- The data is available as of 2024.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is distributed under a MIT license.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No
7. *Any other comments?*
	- None

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- MAL serves as the source of the data. Allen Uy is hosting the dataset at the repo https://github.com/varygx/AnimeAnalysis. 
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- You can contact the author at allenuy0211@gmail.com
3. *Is there an erratum? If so, please provide a link or other access point.*
	- None at the time of writing
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Refer to the repo if any updates are made.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- N/A
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions can technically be accessed via commit history.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- N/A
8. *Any other comments?*
	- None

\newpage

# References

### 2024-04-18 paper/paper.qmd
Linted and styled scripts

@@
 
-# Introduction (longer)
+# Introduction
 
@@
 2.  Except for the oldest anime, anime is popular regardless of age.
-3.  The fraction of people that score an anime to the total members of an anime is a strong indicatowwwwwwwwwr of rating.
+3.  The fraction of people that score an anime to the total members of an anime is a strong indicator of rating.
 
@@
 
-Link to datasheet in repo here
+The datasheet can be found in the repo at [other/datasheet/datasheet.pdf](../other/datasheet/datasheet.pdf)
 

### 2024-04-18 scripts/00-simulate_data.R

@@ -1,14 +1,15 @@
 #### Preamble ####
 # Purpose: Simulates a dataset of anime based on sketches prior to obtaining data.
 # Author: Allen Uy
-# Date: 10 April 2024
+# Date: 17 April 2024
 # Contact: allen.uy@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: None
 
 
 #### Workspace setup ####
-library(tidyverse)
+library("tidyverse")
+
 set.seed(42)
 
 
@@ -30,14 +31,16 @@ data <- tibble(
   genre = random_genres,
   members = round(runif(num_obs, 100, 1000000)),
   popularity = rank(-members),
-  fraction = pmin(pmax(rnorm(num_obs, mean=0.39, sd=0.1), 0), 1)
+  fraction = pmin(pmax(rnorm(num_obs, mean = 0.39, sd = 0.1), 0), 1)
 )
 
 score_distribution_plot <- ggplot(data, aes(x = score)) +
   geom_histogram(binwidth = 0.5, fill = "skyblue", color = "black") +
-  labs(title = "Distribution of Scores",
-       x = "Score",
-       y = "Frequency") +
+  labs(
+    title = "Distribution of Scores",
+    x = "Score",
+    y = "Frequency"
+  ) +
   theme_minimal()
 
 score_distribution_plot
@@ -46,18 +49,18 @@ rank_popularity_plot <- ggplot(data, aes(x = rank, y = popularity)) +
   geom_point(size = 3, color = "darkorange") +
   scale_x_reverse() +
   scale_y_reverse() +
-  labs(title = "Rank vs. Popularity",
-       x = "Rank",
-       y = "Popularity") +
+  labs(
+    title = "Rank vs. Popularity",
+    x = "Rank",
+    y = "Popularity"
+  ) +
   theme_minimal()
 
 rank_popularity_plot
 
-fraction_distribution_plot <- data |> ggplot(aes(x=fraction)) +
-  geom_histogram(binwidth = 0.01, color="darkblue", fill="lightblue") +
+fraction_distribution_plot <- data |> ggplot(aes(x = fraction)) +
+  geom_histogram(binwidth = 0.01, color = "darkblue", fill = "lightblue") +
   labs(x = "Fraction of Scoring Users to List Users", y = "Frequency") +
   theme_minimal()
 
 fraction_distribution_plot
-
-

### 2024-04-18 scripts/01a-download_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data using the MyAnimeList API
 # Author: Allen Uy
-# Date: 12 April 2024
+# Date: 17 April 2024
 # Contact: allen.uy@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: .env is placed in working directory with bearer token
-# refer to README for more details
+# refer to README for more details and for resources to learn how to run the file
 
 
 #### Workspace setup ####
@@ -18,34 +18,36 @@ load_dot_env()
 BEARER_TOKEN <- Sys.getenv("BEARER_TOKEN")
 
 #### Obtain top ranked anime from MyAnimeList ####
-num_anime = 500
-total_anime = 20000
-fields="id,title,rank,start_date,mean,popularity,num_list_users,num_scoring_users,studios,genres"
+num_anime <- 500
+total_anime <- 20000
+fields <- "id,title,rank,start_date,mean,popularity,num_list_users,num_scoring_users,studios,genres"
 
-all_anime <- tibble(id=numeric(),
-                    title=character(),
-                    rank=numeric(),
-                    start_date=character(),
-                    studio=character(),
-                    mean=numeric(),
-                    popularity=numeric(),
-                    num_list_users=numeric(),
-                    num_scoring_users=numeric(),
-                    genres=list())
+all_anime <- tibble(
+  id = numeric(),
+  title = character(),
+  rank = numeric(),
+  start_date = character(),
+  studio = character(),
+  mean = numeric(),
+  popularity = numeric(),
+  num_list_users = numeric(),
+  num_scoring_users = numeric(),
+  genres = list()
+)
 
-for (n in 0:(total_anime/num_anime - 1)) {
-  req = request("https://api.myanimelist.net/v2/anime/ranking") |> 
-    req_url_query(ranking_type="all", limit=num_anime, offset=0+n*500, fields=fields) |>
+for (n in 0:(total_anime / num_anime - 1)) {
+  req <- request("https://api.myanimelist.net/v2/anime/ranking") |>
+    req_url_query(ranking_type = "all", limit = num_anime, offset = 0 + n * 500, fields = fields) |>
     req_auth_bearer_token(BEARER_TOKEN)
-  
+
   resp <- req_perform(req)
-  
+
   anime_json <- resp_body_json(resp)
-  
-  
+
+
   for (i in 1:num_anime) {
[…]

### 2024-04-18 scripts/01b-download_data.R

@@ -1,11 +1,12 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data using the MyAnimeList API
 # Author: Allen Uy
-# Date: 12 April 2024
+# Date: 17 April 2024
 # Contact: allen.uy@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: .env is placed in working directory with bearer token
 # refer to README for more details. 01a-download_data is run.
+# Note: This file is not necessary to run. We did not end up exploring this in the paper
 
 
 #### Workspace setup ####

### 2024-04-18 scripts/02-data_cleaning.R

@@ -5,7 +5,7 @@
 # Date: 12 April 2024
 # Contact: allen.uy@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 01a-download_data is run and raw data is saved in 
+# Pre-requisites: 01a-download_data is run and raw data is saved in
 # appropriate location
 # Update ref_date as needed
 
@@ -14,7 +14,7 @@ library("tidyverse")
 library("arrow")
 library("janitor")
 
-ref_date = as.Date("2024-04-12")
+ref_date <- as.Date("2024-04-12")
 
 
 #### Clean data ####
@@ -42,13 +42,14 @@ cleaned_data$start_date <- as.Date(cleaned_data$start_date)
 cleaned_data$num_scoring_users <- as.integer(cleaned_data$num_scoring_users)
 cleaned_data$num_list_users <- as.integer(cleaned_data$num_list_users)
 
-cleaned_data<- cleaned_data |>
+cleaned_data <- cleaned_data |>
   mutate(days_since_start = as.integer(ref_date - start_date))
 
 cleaned_data <- cleaned_data |>
   mutate(fraction = num_scoring_users / num_list_users)
 
-cleaned_data <- cleaned_data |> select(-genres) |>
+cleaned_data <- cleaned_data |>
+  select(-genres) |>
   clean_names()
 
 # Select only the first 10000 rows based on rank

### 2024-04-18 scripts/03-test_data.R

@@ -12,7 +12,6 @@
 library("tidyverse")
 library("testthat")
 library("arrow")
-library("here")
 
 clean_anime <- read_parquet(here::here("data/analysis_data/clean_anime.parquet"))
 

### 2024-04-18 scripts/04-model.R

@@ -13,6 +13,7 @@ library("tidyverse")
 library("rstanarm")
 library("modelsummary")
 
+
 #### Read data ####
 clean_anime <- read_parquet("data/analysis_data/clean_anime.parquet")
 

### 2024-04-18 paper/paper.qmd
Finished version 1 of paper

@@
 author: Allen Uy
-thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
+thanks: "Code and data are available at: [https://github.com/varygx/AnimeAnalysis](https://github.com/varygx/AnimeAnalysis)"
 date: today
@@
 
-Keywords: anime, regression, MyAnimeList, scoring fraction, rank, popularity, rating
-
 # Introduction
 
-Anime refers to animation originating from Japan.
-(I want to introduce what anime is better).
+In Japan, Anime may refer to any form of animation.
+In English it is commonly used to refer to animation originating from Japan.
+Anime is not much different compared to other forms of media, however anime and animation in general is sometimes regarded by many as 'childish', despite plenty of anime covering serious topics[@enjoyAnimation].
+This may be due to the image of western animation studios.
+Disney and Pixar films are marketed towards children and often are themed around positive messages.
+Violence or mature themes would almost never be included.
+Despite this anime represents a huge market that is projected to grow to almost \$60 billion USD by 2032 [@animeMarket].
+Anime is comparable to primetime network TV shows in the United States by comparing average household rating data [@nielsen, @animetvrating].
 In 2021, half of Netflix's 222 million subscribers watched some anime on the platform and viewership saw an increase of 20% in the total hours over the previous year [@netflixAnime].
-Anime is not much different compared to other forms of media, however anime and animation in general is still often regarded by many as 'childish', despite plenty of anime covering serious topics[@enjoyAnimation].
+Netflix now also creates exclusive Netflix Original anime series.
+
+A core research area for many companies is recommendation.
+Google search engine recommends the most relevant websites, Netflix recommends shows you might enjoy, all to keep users on their platform.
+Good recommendation systems are just as important for companies as they are for users.
+No one wants to be recommended something irrelevant.
+These recommendation systems are built on metrics, which are often kept secret.
+
+What makes an anime good?
+The answer will be different for many people.
+Reviews are subjective, they can be based on quality, enjoyment, or some mixture of the two.
+Rather than qualitatively looking at reviews of anime, what can the numbers tell us about the quality of an anime.
+The estimand of interest is the effect of metrics such as scoring fraction, defined as percentage of people who rate an anime to the total number who have engaged with the anime, and popularity on the rating of anime.
 
@@
 Users are able to keep track of anime they have watched or plan to watch, as well as rate and find similar anime.
-MAL is similar to IMDb in terms of functionality.
-
-The estimand of interest is the effect of
-
-We conduct an analysis on the ratings of anime on MAL. Specifically we contrast
+MAL is similar to IMDb, short for Internet Movie Database, in terms of functionality.
+With just over 16 million users on the site as of April 17, 2024, it serves as the perfect sample of anime viewers.
+We conduct an analysis on the ratings of anime on MAL.
+Specifically we look at the distribution of scores on the platform, the correlation between rank and popularity, and the effect of scoring fraction.
+We then build a model to predict anime rating based on some of these factors.
 
@@
 @sec-model details the construction and methodology of the statistical models used.
-@sec-results presents the key findings of our analysis, while @sec-discussion critically reviews the content, addresses the implications of the results, acknowledges model limitations, and suggests potential research directions.
+@sec-results presents the findings of our model, while @sec-discussion goes over the key findings, addresses implications and applications, acknowledges weaknesses, and suggests potential research directions.
 
@@
 
+## Measurement
+
 The data in this paper is sourced from the MAL API [@MALAPI] and was gathered on April 12, 2024.
 The rankings of anime in the database are updated twice a day so the data gathered can be assumed to be up to date.
-Data analysis is performed in R [@citeR] with help from the following libraries: `tidyverse` [@citeTidyverse], `arrow` [@citeArrow], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `testthat` [@citeTestthat], `here` [@citeHere], `knitr` [@citeKnitr], `kableExtra` [@citeKableExtra], `dotenv` [@citeDotenv], and `httr2` [@citeHttr2].
-
-## Measurement
-
 In order to rate anime and add them to a list users must register an account on the MAL website.
@@
 Every user that has an anime on their list is counted as a member of that anime, which is how the popularity rank is calculated.
-The user can also give a score to an anime, regardless of status, which is an integer from 1 to 10.
+The user can also give a rating to an anime, regardless of status, which is an integer from 1 to 10.
 The score of an anime on MAL is a weighted score calculated via the following:
@@
 Due to the personal nature of these lists we assume that each user and list is associated with exactly one individual.
+In short, the data used in this paper is calculated by MAL through their database system, which we assume to be correct and transparent.
 
@@
 It is also sensible that the mean score of the top 10000 anime is closer to 7 than to 5.
-Scores are inherently a subjective opinion and may take into account enjoyability, as well as how 'good' the piece of work is.
+Scores are inherently a subjective opinion and may take into account enjoyment, as well as how 'good' the piece of work is.
 Many people could enjoy a bad show even despite having many flaws.
@@
 #| label: fig-score_distribution
-#| fig-cap: Distribution of Scores of Top 10000 Anime
+#| fig-cap: Distribution of Scores of Top 10000 Anime. Note the right-skewedness, it is hard to be a highly rated anime.
 
@@
 #| label: fig-rank_vs_popularity
-#| fig-cap: Rank vs Popularity for Top 10000 Anime
+#| fig-cap: Rank vs Popularity for Top 10000 Anime. A simple linear model fitted to the data highlights the relationship between rating and popularity.
 
@@
 #| label: fig-date_relationships
-#| fig-cap: "Correlation to Date"
+#| fig-cap: "Metrics of anime compared to their start date"
 #| fig-subcap: ["Popularity plot", "Rank plot"]
@@
 #| label: fig-date_relationships_modern
-#| fig-cap: "Correlation to Modern Dates"
+#| fig-cap: "Metrics of modern post-2000s anime compared to their start date"
 #| fig-subcap: ["Popularity plot", "Rank plot"]
@@
 On average, 39% of users end up rating an anime on their list according to @fig-scoring_fraction.
+Scoring fraction seems to follow a normal distribution.
 There is a strong positive correlation between scoring fraction and popularity as seen in @fig-fraction_relationships-1, which is sensible as fans of an anime or any media in general are likely express their opinion on that particular media.
@@
 #| label: fig-fraction_relationships
-#| fig-cap: "Correlation to Scoring Fraction"
+#| fig-cap: "Metrics of anime compared to scoring fraction"
 #| fig-subcap: ["Popularity plot", "Rank plot"]
@@
 ```
+
+## Code
+
+Data analysis is performed in R [@citeR] with help from the following libraries: `tidyverse` [@citeTidyverse], `arrow` [@citeArrow], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `testthat` [@citeTestthat], `here` [@citeHere], `knitr` [@citeKnitr], `kableExtra` [@citeKableExtra], `dotenv` [@citeDotenv], and `httr2` [@citeHttr2].
 
@@
 ### Model Justification
+
+Since we are aiming to model a continuous variable representing the mean user score of an anime, regression becomes our preferred method.
+We aim for a relatively simple model in multiple linear regression using just 3 variables, with the hopes of being able to explain the rating of an anime using only the most important relations.
+Including too many variables in our model may lead to overfitting.
+We aim to create a model that can generalize not only across different anime but also potentially across other forms of media.
 
@@
 
+### Relationship between Rank and Popularity
+
+Based on @sec-rank-and-popularity there is a clear relation between the mean user score of anime on MAL and its popularity.
+However there is noise regarding that relationship.
+How much of popularity is due to rating and how much of rating is due to popularity are areas of interest.
+A qualitative analysis through a survey on the perception of anime quality and popularity would be useful here.
+A sufficiently large fanbase could rate an anime higher based on enjoyment which would not necessarily be wrong.
+
+### Anime remains consistently popular
+
+The quality of anime has remained relatively consistent in modern times.
+There is a slight increase in the ranking of recent anime which could be attributed to recency bias.
+The oldest anime rated lower and were much less popular, perhaps due to generational differences.
+There is still many anime that have yet to air that originate from popular novels or manga (a style of Japanese comic).
+These works offset some of the more generic anime that have released.
+Isekai, which means "another world", is a popular genre of anime which has multiple shows every season.
+Many of these shows may appear low quality due to the repeated shared elements and tropes between them, yet they still remain popular.
+
+### The Importance of Scoring Fraction
+
+We find that scoring fraction is the largest indicator of mean user rating on MAL.
+The correlation found in @sec-scoring-fraction is surprising as it is contrary to human psychology.
+People are more likely to remember negative experiences so one might expect an increase in scoring fraction for low quality anime @negativeExperience.
+However we find the opposite on MAL, suggesting people are less likely to rate low quality anime, perhaps as a way to forget about the show.
+
+### Modelling
+
 Through a multiple linear regression model built in @sec-model, we find that the base anime is given a score of 6.34.
@@
 For every 1 million members of an anime its score increases by 0.7776.
-
-The correlation found in @sec-scoring-fraction is surprising as it is contrary to human psychology.
-People are more likely to remember negative experiences so one might expect an increase in scoring fraction for low quality anime @negativeExperience.
-However we find the opposite on MAL, suggesting people are less likely to rate low quality anime, perhaps as a way to forget about the show.
 
@@
 
-There is some noise regarding the relationship between rating and popularity.
-How much of popularity is due to rating and how much of rating is due to popularity are areas of interest.
 We assume that each user on MAL is a unique individual due to the personal nature of lists.
 It would not generally serve much purpose for a person to keep track of separate lists.
-However in the past there have been issues of people attempting to artificially lower or raise the scores of some anime @MALBrigading.
+In the past there have been issues of people attempting to artificially lower or raise the scores of some anime @MALBrigading.
+This form of brigading and manipulation was common between fanbases of anime that might not have agreed with each other.
 Since then MAL has attempted to police this issue and we do not believe it should be a concern in this dataset.
@@
 Analysis of a graph structure could prove interesting, especially in the context of recommendations and series of anime.
+It would be interesting to look at series of anime and see how its rating and popularity change over time as more seasons are released.
 
 A variable that would likely be helpful in our model is drop rate, which can be calculated as the fraction of users that label an anime as dropped compared to the total members of that anime.
-As mentioned previously this variable is capable of being retrieved from the API but would take a long time to gather.
-We believe that higher ranked anime are likely to correspond to lower drop rate.
+As mentioned previously this variable is capable of being retrieved from the API but would take a long time to gather due to the API call limit.
+We believe that higher ranked anime are likely to correspond to lower drop rate but would like to confirm this.
 
-An analysis on scoring fraction should be done on IMDb if applicable to verify whether the assumptions made in this paper apply to other forms of media beyond anime.
+Instead of looking at popularity as the total number of users that have listed an anime, we can try calculating popularity by dividing by the length of time an anime has been out.
+This may solve the issue of our model underrating highly rated anime that have been out for only a short amount of time.
+
+An analysis on scoring fraction should be done on IMDb to verify whether the assumptions made in this paper apply to other forms of media beyond anime.
+Does our analysis also apply if we look at different genres of anime.
 
@@
 
-# R package
-
-TODO: create package
-
 \newpage

### 2024-04-19 other/datasheet/datasheet.qmd
Removed extraneous section and fixed date for datasheet

@@
 thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
-date: "`r Sys.time()`"
-date-format: "D MMMM YYYY"
+date: today
+date-format: long
 format: pdf
